Stage-Splitting a Modal Language

### 2014-08-30 paper/splitting.tex
fixed up the partial value splitting section

As with the dynamics, our stage-splitting algorithm for expressions in \lang\ take 
the form of two mutually-dependent judgments, $\splitonesym$ and $\splittwosym$. 
Before diving into the full generality, we consider splitting for a simple fragment of the full language: partial values.

@@

Before getting into the formal presentation, 
we first consider the problem of splitting stage-\bbone\ partial values.
This serves as a didactic stepping-stone to full term-splitting, 
and it is a necessary component of the correctness theorem.

The rules for partial value splitting are given in \cref{fig:valSplit}.  It consists of a single judgment, $v \vsplito [v_1,v_2]$,
which sends a partial value $v$ to two single-stage values $v_1$ and $v_2$. 
Those respectively represent the stage-\bbone\ and stage-\bbtwo\ content of the original partial value.  
At base types, partial value splitting assigns all content to stage \bbone, and puts in a nullary tuple for stage two,
in accordance with the precept that base types have only trivial content at stage \bbtwo.
Splitting acts distributively at product, sum, and recursive types.
Functions split into two other functions.  Since the body of a function is an open term, this rule must rely on 
general term splitting, which is covered momentarily.

Lastly, we consider value splitting at the $\fut$ type.  The only partial value with this type
is a $\next$ block containing a reference into the future environment.  This splits into a 
nullary tuple and the same variable, again aligning with the precept that $\fut$ types contain trivial stage-\bbone\
content.

>>>>

As with the dynamics, our stage-splitting algorithm for expressions in \lang\ take 
the form of two mutually-dependent judgments, $\splitonesym$ and $\splittwosym$. 
Before diving into the full generality, we consider splitting for a simple fragment of the full language: partial values.
After that, we define splitting for full expressions, discuss some notable properties of the algorithm, and then prove correctness.

@@

We now consider the problem of splitting stage-\bbone\ partial values.
This serves as a simple didactic stepping-stone to the full formulation, 
and we will see later that it is a necessary component of the correctness theorem.

The basic goal of partial value splitting is to take a partial value $v$ and create from it two single stage values $v_1$ and $v_2$,
where $v_1$ contains only the information from $v$ that is relevant to the first stage, 
and $v_2$ contains only the information from $v$ that is relevant to the second stage.
There are many reasonable ways to do this, 
and we simply chose one that preserves as much structure as possible from $v$.
Formally, partial value splitting comprises a single judgment, $v \vsplito [v_1,v_2]$, the rules for which are given in \cref{fig:valSplit}.
It essentially acts distributively at product, sum, and recursive types, 
doing little more than recuring into subvalues and duplicating the structure to both results.
At base types, partial value splitting assign all content ({\em i.e.} the integer or boolean) to stage \bbone, and uses a nullary tuple placeholder for stage \bbtwo.
Conversely at $\fut$ types, splitting assigns all content ({\em i.e.} the environment reference) to stage \bbtwo, and uses a nullary tuple for stage \bbone.

Functions are inherently more complicated. 
Since the body of a function is an open term, the partial value splitting rule for functions must rely on general expression splitting, which is covered momentarily.
The most we can say here is a function splits into two other functions, 
whose bodies correspond to the stage \bbone\ and stage \bbtwo\ components of the original function's body.
